---
title: "Conservation Agents Leaderboard"
output:
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    storyboard: true
    theme: 
      bootswatch: cosmo
      
    navbar:
    - { title: "Fishing", href: "fishing.html"}
    - { title: "Conservation", href: "conservation.html"}
    - { title: "Climate", href: "climate.html"}
    - { title: "Wildfire", href: "wildfire.html"}
    - { title: "Epidemics", href: "epidemic.html"}
    - { title: "Submit Agent", href: "https://forms.gle/tdVmyo4JD7cS4Goo7", 
        target: "_blank", icon: "fa fa-paper-plane"}
    - {icon: "fab fa-github", href: "https://github.com/boettiger-lab/rl-leaderboard",
        target: "_blank"}
---
```{r, include=FALSE}
library(dplyr)
library(flexdashboard)
library(DT)
source("utils.R")

conservation_leaderboard <- select_gym_leaderboard("Gym Conservation")
```   


### conservation-v0 {data-commentary-width=400}

```{r} 
display_env_leaderboard(conservation_leaderboard, 'conservation-v0')
```

***

conservation-v0 considers a single species conservation problem in which the agent can increase the population at a cost.

**Observation Space** The agent observes the population at that time step.

**Model Dynamics** Dynamics follow a Ricker model.

**Action Space** The agent determines how much to increment the population. 

**Reward Function** The agent is rewarded proportionally to the population level and penalized according to the magnitude of the action.

---
[Conservation Gym](https://github.com/boettiger-lab/gym_conservation)


### conservation-v2 {data-commentary-width=400}

```{r} 
display_env_leaderboard(conservation_leaderboard, 'conservation-v2')
```

***

conservation-v2 considers a single species conservation problem in which the agent can increase the population at a cost.

**Observation Space** The agent observes the population at that time step.

**Model Dynamics** Dynamics follow a May model.

**Action Space** The agent determines how much to increment the population. 

**Reward Function** The agent is rewarded proportionally to the population level and penalized according to the magnitude of the action.

---
[Conservation Gym](https://github.com/boettiger-lab/gym_conservation)


### conservation-v3 {data-commentary-width=400}

```{r} 
display_env_leaderboard(conservation_leaderboard, 'conservation-v3')
```

***

conservation-v3 considers a single species conservation problem that has a non-stationary model. 

**Observation Space** The agent observes the population at that time step.

**Model Dynamics** Dynamics follow a May model in which a parameter, $a$, continually changes, making it more likely for the population to collapse.

**Action Space** The agent determines how much to increment the population.

**Reward Function** The agent is rewarded proportionally to the population level and penalized according to the magnitude of the action.

---
[Conservation Gym](https://github.com/boettiger-lab/gym_conservation)


### conservation-v5 {data-commentary-width=400}

```{r} 
display_env_leaderboard(conservation_leaderboard, 'conservation-v5')
```

***

conservation-v5 considers a single species conservation problem that has a non-stationary model. 

**Observation Space** The agent observes the population at that time step.

**Model Dynamics** Dynamics follow a May model in which a parameter, $a$, continually changes, making it more likely for the population to collapse.

**Action Space** The agent determines how much to decrease the parameter $a$ and move the system away from the tipping point.

**Reward Function** The agent is rewarded proportionally to the population level and penalized according to the magnitude of the action.

---
[Conservation Gym](https://github.com/boettiger-lab/gym_conservation)


### conservation-v6 {data-commentary-width=400}

```{r} 
display_env_leaderboard(conservation_leaderboard, 'conservation-v6')
```

***

conservation-v6 considers a single species conservation problem that has a non-stationary model. 

**Observation Space** The agent observes the population at that time step.

**Model Dynamics** Dynamics follow a May model in which a parameter, $a$, continually changes, making it more likely for the population to collapse. There is some stochasticity in this model, differentiating it from `conservation-v5`.

**Action Space** The agent determines how much to decrease the parameter $a$ and move the system away from the tipping point.

**Reward Function** The agent is rewarded proportionally to the population level and penalized according to the magnitude of the action.

---
[Conservation Gym](https://github.com/boettiger-lab/gym_conservation)


### conservation-v7 {data-commentary-width=400}

```{r} 
display_env_leaderboard(conservation_leaderboard, 'conservation-v7')
```

***

conservation-v7 considers a conservation problem that has a non-stationary model. It is similar to conservation-v5 but works on an ensemble of populations. By default, the replicate number is 1, so the default is equivalent to conservation-v5.

**Observation Space** The agent observes the populations at that time step.

**Model Dynamics** Dynamics follow a May model in which a parameter, $a$, continually changes, making it more likely for the populations to collapse.

**Action Space** The agent determines how much to decrease the parameter $a$ and move the systems away from their tipping points.

**Reward Function** The agent is rewarded proportionally to the mean population level and penalized according to the magnitude of the action.

---
[Conservation Gym](https://github.com/boettiger-lab/gym_conservation)

