---
title: "Conservation Agents Leaderboard"
output:
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    storyboard: true
    theme: 
      bootswatch: cosmo
      
    navbar:
    - { title: "Fishing", href: "fishing.html", target: "_blank"}
    - { title: "Conservation", href: "conservation.html", target: "_blank"}
    - { title: "Climate", href: "climate.html", target: "_blank"}
    - { title: "Wildfire", href: "wildfire.html", target: "_blank"}
    - { title: "Epidemics", href: "epidemic.html", target: "_blank"}
    - { title: "Submit Agent", href: "https://forms.gle/tdVmyo4JD7cS4Goo7", 
        target: "_blank", icon: "fa fa-paper-plane"}
    - {icon: "fab fa-github", href: "https://github.com/boettiger-lab/rl-leaderboard",
        target: "_blank"}
---
```{r, include=FALSE}
library(dplyr)
library(flexdashboard)
library(DT)
library(crosstalk)
library(reticulate)
source("utils.R")

fishing_leaderboard <- select_gym_leaderboard("Gym Fishing")
```

  
### fishing-v1 


```{r} 
display_env_leaderboard(fishing_leaderboard, 'fishing-v1')
``` 

***


This environment implements a simple, single species logistic growth-based fishery.

**Observation Space** The agent observes the fish population at that time step.

**Model Dynamics** Dynamics follow a logistic growth model.

**Action Space** The agent selects a quantity of fish to harvest with respect to K with a continuous interval.

**Reward Function** The agent is rewarded by the amount of fish harvested at a time step.



### fishing-v2 


```{r} 
display_env_leaderboard(fishing_leaderboard, 'fishing-v2')
``` 

***

This environment implements a single species logistic growth-based fishery with a tipping point.

**Observation Space** The agent observes the fish population at that time step.

**Model Dynamics** Dynamics follow a logistic growth model but below a population of 0.5K the population becomes much more likely to crash.

**Action Space** The agent selects a quantity of fish to harvest with respect to K with a continuous interval.

**Reward Function** The agent is rewarded by the amount of fish harvested at a time step.


