---
title: "Conservation Agents Leaderboard"
output:
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    storyboard: true
    theme: 
      bootswatch: cosmo
      
    navbar:
    - { title: "Fishing", href: "fishing.html", target: "_blank"}
    - { title: "Conservation", href: "conservation.html", target: "_blank"}
    - { title: "Climate", href: "climate.html", target: "_blank"}
    - { title: "Wildfire", href: "wildfire.html", target: "_blank"}
    - { title: "Epidemics", href: "epidemic.html", target: "_blank"}
    - { title: "Submit Agent", href: "https://forms.gle/tdVmyo4JD7cS4Goo7", 
        target: "_blank", icon: "fa fa-paper-plane"}
    - {icon: "fab fa-github", href: "https://github.com/boettiger-lab/rl-leaderboard",
        target: "_blank"}
---
```{r, include=FALSE}
library(dplyr)
library(flexdashboard)
library(DT)
library(crosstalk)
source("utils.R")

wildfire_leaderboard <- select_gym_leaderboard("Gym Wildfire")
```   


### wildfireCA-v0 {data-commentary-width=400}

```{r}
display_env_leaderboard(wildfire_leaderboard, "wildfireCA-v0")
```

***

wildfireCA-v0 is based on a wildfire cellular automata model from [Alexandridis et al.](https://www.sciencedirect.com/science/article/abs/pii/S0096300308004943) 

**Observation Space** The problem according to default settings is a 36 x 36 grid wherein each cell can be in one of four states: no fuel, unburned fuel, ignited or burned. The agent observes a vector that gives the state of each grid cell.  

**Model Dynamics** The dynamics here are quite simple: if one cell is ignited, then there will be some probability that a neighboring cell ignite at the next time step. By default, there is some wind in this environment so there is a directional bias for ignition probability.

**Action Space** By default, the agent is allowed to do 8 preventative burns per evolution time step. A preventative burn turns an unburned active fuel cell into a burned cell. 

**Reward Function** The agent is penalized by the amount of actively burning grid cells at each evolution time step. 

